Using Genetic Algorithms to Find Approximations for the Minimum Vertex Cover Problem

### 2018-02-24 paper.tex
will change figures to table
will do authors the right way

% including packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{hyperref}
\usepackage{hypcap}
\usepackage[autostyle]{csquotes}
\usepackage[]{biblatex}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage[end]{algpseudocode}
\usepackage{caption}

% preferences
\graphicspath{ {images/} }
\newcommand{\lineSeparationLength}{2mm}
\hypersetup{colorlinks=true, allcolors=black}
\addbibresource{references.bib}
\ExecuteBibliographyOptions{
	giveninits=true,
	isbn=false,
	doi=false,
	url=false
}
\setlength{\parskip}{1em}
\newcommand{\textem}[1]{\textbf{\textit{#1}}}
\newtheorem{lemma}{Lemma}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\algnewcommand\algorithmicto{\textbf{to}}
\algrenewtext{For}[3]%
{\algorithmicfor\ #1 = #2 \algorithmicto\ #3 \algorithmicdo}

@@

@@

\section{Experimental Results}
\label{sec:er}
\setcounter{figure}{0}
\captionsetup[figure]{name={Table}}
For the experimental tests,
the genetic algorithm software package GENEsYs is used [1]misp.
This implementation is based on the widely used GENESIS software by Grefenstette
(see [3], pp. 374-377 misp), but allows for more 
flexibility concerning genetic operators and data monitoring.
The parameter settings for our experiments are
given in section~\ref{sec:GAmvcp}.

Multiple problem instances are used to demonstrate the applicability of GAs to tackle the mvcp
The results in table~\ref{fig:t1}
and table~\ref{fig:t2} correspond to the first test set, which consists of
five random graphs of size $n = 100$ with different
edge densities $d$, $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$, are used.
An edge density of $d = 0.1$ means that an edge is placed between two
nodes with a probability of 0.1.
Moreover we construct the graphs in a way that guarantees an optimum of quality 55
(we set $k = 55$ in algorithm~\ref{alg:gen}).
In addition to the regular graphs introduced by
Papadimitriou and Steiglitz and described in section~\ref{sec:ra}.
Recall that these graphs contain $n=3k+4 (k \geq 1)$ nodes distributed on three levels.
They can be scaled up by choosing high values for $k$.
A graph instance of the regular graph of size $n = 100 (k=32)$ is chosen.

@@

For each of these graphs, a total of
$N = 100$ independent runs of the genetic algorithm is performed.
The results are summarized in table~\ref{fig:t1} for the best
fitness values that were encountered during the 100 runs.
For each problem instance, the different fitness values that were
obtained and their frequencies are recorded.
Furthermore, the average fitness value $\bar{f}$ over
all 100 runs is indicated at the bottom of the table.
For example, the first column in table~\ref{fig:t1} indicates
that the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 53$,
the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 54$,
the best obtained fitness value in 3 of the 100 runs was $f(\vec{x}) = 55$, and so on...
And the average of these values is indicated by $\bar{f}$, which is the average value of
the best obtained fitness values over the 100 runs.

As a termination criterion for the genetic algorithm, a bound for the total number of function evaluations is set.
For example The total number of function evaluations per single run is chosen to be $2 \cdot 10^4$ in table~\ref{fig:t1}.
That is, the algorithm terminates when $2 \cdot 10^4$ evaluations of the fitness function
had occurred.
This bound is indicated as an index $t$ in the notation $f_t(\vec{x})$.
Consequently, only a small fraction of the search space is explored by the genetic algorithm.
This fraction is about $ 2 \cdot 10^4 / 2^{100} \approx 1.6 \cdot 10^{-24} \% $ for the first test set.
and it is about $ 4 \cdot 10^4 / 2^{200} \approx 2.5 \cdot 10^{-54} \% $ for the second test set.

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t1}
\caption{general schema for genetic algorithms}
\label{fig:t1}
\end{figure}

For each of the problems in the first test set, a total of $N=100$
independent runs of the vercov algorithm is performed. The results are summarized in table~\ref{fig:t2}.
Notice that for one problem instance, the results may differ in each run due to the
non-determinism of the algorithm (see algorithm~\ref{alg:vercov} line~\ref{alg:rand}).

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t2}
\caption{general schema for genetic algorithms}
\label{fig:t2}
\end{figure}

To test the behaviour of the genetic algorithm
as well as the vercov algorithm for an even
larger problem size, The same experiments were performed for larger graphs
The results in table~\ref{fig:t3}
and table~\ref{fig:t4} correspond to the second test set, which consists of
five random graphs of size $n = 200$ with different
edge densities $d$, $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$, are used.
Moreover we construct the graphs in a way that guarantees an optimum of quality 110
(see algorithm~\ref{alg:gen}).
In addition to a graph instance of the regular graphs introduced by
Papadimitriou and Steiglitzof of size $n = 220 (k=66)$.
In this case, the genetic algorithm
was allowed to run for $4 \cdot 10^4$ function evaluations.
The corresponding results obtained by the
genetic algorithm are shown in table~\ref{fig:t3}, while the results
from the vercov algorithm are presented in table~\ref{fig:t4}.
See the previous paragraphs for a better understanding of these results.

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t3}
\caption{general schema for genetic algorithms}
\label{fig:t3}
\end{figure}

\begin{figure}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t4}
\caption{general schema for genetic algorithms}
\label{fig:t4}
\end{figure}

>>>>

% including packages
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{wrapfig}
\usepackage[a4paper, total={6in, 8in}]{geometry}
\usepackage{hyperref}
\usepackage[all]{hypcap}
\usepackage[autostyle]{csquotes}
\usepackage[]{biblatex}
\usepackage{amsfonts}
\usepackage{algorithm}
\usepackage[end]{algpseudocode}
\usepackage{caption}

% preferences
\graphicspath{ {images/} }
\newcommand{\lineSeparationLength}{2mm}
\hypersetup{colorlinks=true, allcolors=black}
\addbibresource{references.bib}
\ExecuteBibliographyOptions{
	giveninits=true,
	isbn=false,
	doi=false,
	url=false
}
\setlength{\parskip}{1em}
\newcommand{\textem}[1]{\textbf{\textit{#1}}}
\newtheorem{lemma}{Lemma}
\renewcommand{\thefootnote}{\fnsymbol{footnote}}
\algnewcommand\algorithmicto{\textbf{to}}
\algrenewtext{For}[3]%

@@

% List of Figures and Tables
\cleardoublepage\phantomsection\addcontentsline{toc}{section}{List of Figures}
\listoffigures

\phantomsection\addcontentsline{toc}{section}{List of Tables}
\listoftables

\phantomsection\addcontentsline{toc}{section}{List of Tables}
\section*{abbrevs}  % Set the left side page header to "Abbreviations"
\begin{center}
\begin{tabular}{ l c } 
 GA & Genetic Algorithm \\ 
 cell4 & cell5 \\ 
 cell7 & cell8
\end{tabular}
\end{center}

@@

\section{Experimental Results}
\label{sec:er}
For the experimental tests,
the genetic algorithm software package GENEsYs is used [1]misp.
This implementation is based on the widely used GENESIS software by Grefenstette
(see [3], pp. 374-377 misp), but allows for more 
flexibility concerning genetic operators and data monitoring.
The parameter settings for our experiments are
given in section~\ref{sec:GAmvcp}.

Multiple problem instances are used to demonstrate the applicability of GAs to tackle the mvcp
The results in table~\ref{tbl:t1}
and table~\ref{tbl:t2} correspond to the first test set, which consists of
five random graphs of size $n = 100$ with different
edge densities $d$, $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$, are used.
An edge density of $d = 0.1$ means that an edge is placed between two
nodes with a probability of 0.1.
Moreover we construct the graphs in a way that guarantees an optimum of quality 55
(we set $k = 55$ in algorithm~\ref{alg:gen}).
In addition to the regular graphs introduced by
Papadimitriou and Steiglitz and described in section~\ref{sec:ra}.
Recall that these graphs contain $n=3k+4 (k \geq 1)$ nodes distributed on three levels.
They can be scaled up by choosing high values for $k$.
A graph instance of the regular graph of size $n = 100 (k=32)$ is chosen.

@@

For each of these graphs, a total of
$N = 100$ independent runs of the genetic algorithm is performed.
The results are summarized in table~\ref{tbl:t1} for the best
fitness values that were encountered during the 100 runs.
For each problem instance, the different fitness values that were
obtained and their frequencies are recorded.
Furthermore, the average fitness value $\bar{f}$ over
all 100 runs is indicated at the bottom of the table.
For example, the first column in table~\ref{tbl:t1} indicates
that the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 53$,
the best obtained fitness value in 1 of the 100 runs was $f(\vec{x}) = 54$,
the best obtained fitness value in 3 of the 100 runs was $f(\vec{x}) = 55$, and so on...
And the average of these values is indicated by $\bar{f}$, which is the average value of
the best obtained fitness values over the 100 runs.

As a termination criterion for the genetic algorithm, a bound for the total number of function evaluations is set.
For example The total number of function evaluations per single run is chosen to be $2 \cdot 10^4$ in table~\ref{tbl:t1}.
That is, the algorithm terminates when $2 \cdot 10^4$ evaluations of the fitness function
had occurred.
This bound is indicated as an index $t$ in the notation $f_t(\vec{x})$.
Consequently, only a small fraction of the search space is explored by the genetic algorithm.
This fraction is about $ 2 \cdot 10^4 / 2^{100} \approx 1.6 \cdot 10^{-24} \% $ for the first test set.
and it is about $ 4 \cdot 10^4 / 2^{200} \approx 2.5 \cdot 10^{-54} \% $ for the second test set.

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t1}
\caption{general schema for genetic algorithms}
\label{tbl:t1}
\end{table}

For each of the problems in the first test set, a total of $N=100$
independent runs of the vercov algorithm is performed. The results are summarized in table~\ref{tbl:t2}.
Notice that for one problem instance, the results may differ in each run due to the
non-determinism of the algorithm (see algorithm~\ref{alg:vercov} line~\ref{alg:rand}).

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t2}
\caption{general schema for genetic algorithms}
\label{tbl:t2}
\end{table}

To test the behaviour of the genetic algorithm
as well as the vercov algorithm for an even
larger problem size, The same experiments were performed for larger graphs
The results in table~\ref{tbl:t3}
and table~\ref{tbl:t4} correspond to the second test set, which consists of
five random graphs of size $n = 200$ with different
edge densities $d$, $d \in \{0.1, 0.2, 0.3, 0.4, 0.5\}$, are used.
Moreover we construct the graphs in a way that guarantees an optimum of quality 110
(see algorithm~\ref{alg:gen}).
In addition to a graph instance of the regular graphs introduced by
Papadimitriou and Steiglitzof of size $n = 220 (k=66)$.
In this case, the genetic algorithm
was allowed to run for $4 \cdot 10^4$ function evaluations.
The corresponding results obtained by the
genetic algorithm are shown in table~\ref{tbl:t3}, while the results
from the vercov algorithm are presented in table~\ref{tbl:t4}.
See the previous paragraphs for a better understanding of these results.

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t3}
\caption{general schema for genetic algorithms}
\label{tbl:t3}
\end{table}

\begin{table}[!htbp]
\centering
\includegraphics[width=1\textwidth]{t4}
\caption{general schema for genetic algorithms}
\label{tbl:t4}
\end{table}
